Sulfur Dioxide on Water's Surface

### 2011-02-24 TransitOrientation.tex
Added new transit orientation plots, and the Tarbuck references. About to work on the transit orientation text.
New transit images for orientation using new normalization scheme for 2d histograms

	The orientation of a \suldiox~molecule adsorbing to an aqueous surface was determined through an analysis process to find the angles $\theta$ and $\phi$ (figure \ref{fig:water-angles}). For each timestep of the SMD simulations the orientation angles were determined for the transiting \suldiox~as it was pulled into the water slab from the gas phase, both in the neat-water and saturated slab systems. The angle cosine values were collected for the 50 simulations for both systems, and the binned with the position of the \suldiox~relative to the water slab surface location. The resulting 2-dimensional histograms shown in figure \ref{fig:so2-transit-angles} show the orientation trend for the \suldiox~in the gas phase (above 0\angs), near the aqueous surface (near 0\angs), and after entering the water bulk (below 0\angs). Only the surface into which the transiting \suldiox~was steered is shown for the saturated system.

\begin{figure}[h!]
	\begin{center}
		\includegraphics[scale=1.0]{images/so2-angles/so2-angles-transit.png}
		\caption{\suldiox~molecular orientation distributions during SMD transit simulations into an aqueous slab. Both the neat-water (top row) and saturated (bottom row) data sets were analyzed to determine the angles $\theta$ (left column), and $\phi$ (right column) of the transiting \suldiox. The distributions show angle cosines plotted against the distance of the \suldiox~to the location of the water surface. The data sets were averaged at each distance for the respective 50 simulations.}
		\label{fig:so2-transit-angles}
	\end{center}
\end{figure}

	%From its starting position 20\angs above the water surface, until the \suldiox~moves to within 5\angs of the surface of both systems, the orientation is isotropic in both $\theta$ and $\phi$. Upon approaching the saturated surface at approx. 5\angs, the \suldiox~$\phi$ orientation distribution begins to cluster near $\cos(\phi)=1$, with the $\theta$ distribution remaining more isotropic, but with a trend of $\cos(\theta)>0$. At 5\angs the \suldiox~begins interacting with the other \suldiox~molecules that sit atop the water, and the resulting orientation distribution suggests that contact with the \suldiox~layer causes the adsorbing molecule to lie more flat to the surface. Within this same region from 0-5\angs above the surface, the $\phi$ distribution of the neat-\wat~system remains isotropic. The intensity of the distribution (darker blue) also indicates that the \suldiox~spends little time in this region, as it is quickly adsorbed further into the water bulk.

>>>>

	The orientation of a \suldiox~molecule during adsorption to, and absorbtion in an aqueous surface was determined through an analysis of the transit SMD simulations. The angles $\theta$ and $\phi$ (figure \ref{fig:water-angles}) were calculated for each timestep of the SMD simulations as the transiting \suldiox~was pulled into the water slab from the gas phase, both in the neat-water and saturated slab systems. The angle cosine values were collected for the 50 simulations of both systems for each distance from the water surface, resulting in the 2-dimensional histograms shown in figure \ref{fig:so2-transit-angles}. Only the surface into which the transiting \suldiox~was steered into is shown for the saturated system's analysis.

\begin{figure}[h!]
	\begin{center}
		\includegraphics[scale=1.0]{images/transit-so2-angles/so2-angles-transit.png}
		\caption{\suldiox~molecular orientation distributions during SMD transit simulations into an aqueous slab. Both the neat-water (top row) and saturated (bottom row) data sets were analyzed to determine the angles $\theta$ (left column), and $\phi$ (right column) of the transiting \suldiox. The distributions show angle cosines plotted against the distance of the \suldiox~to the location of the water surface. The data sets were averaged at each distance for the respective 50 simulations.}
		\label{fig:so2-transit-angles}
	\end{center}
\end{figure}

	From its starting position 20\angs above the water surface, until the \suldiox~moves to within 10\angs of the surface of both systems, the orientation is isotropic in $\phi$. The trend for the bisector angle, $\theta$, upon approaching the surface is to become more perpendicular to the surface with the \suldiox~sulfur pointing into the water phase. At the point when the \suldiox~reaches the surface location (distance$=0$), the bisector is mostly perpendicular in both the neat-water and saturated systems. In the distribution of $\phi$, both systems show isotropy in the orientation

  Upon approaching the saturated surface at approx. 5\angs, the \suldiox~$\phi$ orientation distribution begins to cluster near $\cos(\phi)=1$, with the $\theta$ distribution remaining more isotropic, but with a trend of $\cos(\theta)>0$. At 5\angs the \suldiox~begins interacting with the other \suldiox~molecules that sit atop the water, and the resulting orientation distribution suggests that contact with the \suldiox~layer causes the adsorbing molecule to lie more flat to the surface. Within this same region from 0-5\angs above the surface, the $\phi$ distribution of the neat-\wat~system remains isotropic. The intensity of the distribution (darker blue) also indicates that the \suldiox~spends little time in this region, as it is quickly adsorbed further into the water bulk.
